Below are 2 linear abstract data modules, whose element is \verb|stduint|.





\subsubsection{Strpage : Dynamic Block Set}

\textbf{\$New}$() \rightarrow *$



\textbf{\$Free}$(*)$



\textbf{\$Get}$(*, idx) \rightarrow stduint$



Get the value in the position of Strpage.



\textbf{\$Set}$(*, idx, val) \rightarrow *'$



Set the value in the position of Strpage.

Return the pointer to the ultimate manager of Strpage.

Then we should access inside data with new but old manager.





\subsubsection{Strbuff}

\textbf{\$New}$(elm\_len) \rightarrow *$



\textbf{\$Free}$(*)$



\textbf{\$Rewind}$(*)$



Move the read pointer (Q) to the beginning (index zero).



\textbf{\$Ealloc}$(*) \rightarrow pureptr$



Allocate an element and return its pointer.



\textbf{\$Send}$(*, *src, len)$



Send bytes but elements.



\textbf{\$Sendx}$(*, stduint pos, *src, len)$



Send bytes but elements, into the position in the \textit{strbuff}.



\textbf{\$SendFile}$(*, FILE*)$



\textbf{\$Send}\textit{N}$(*, \{N\})$



N can be:

\begin{itemize}

\item 8, 16, 32

\item 64 if \verb|_BIT_SUPPORT_64| defined

\item Std for stduint

\item Wleb128u for unsigned Little-Endian Base 128 bytes

\item Wleb128s for   signed Little-Endian Base 128 bytes

\end{itemize}

\textbf{\$Eread}$(*) \rightarrow pureptr$ Element Read



Read an element and return its pointer.

This will make read pointer advance.



\textbf{\$Read}$(*, stduint* lenp) \rightarrow const\ void*$



\verb|lenp| cannot be a nullptr.

Read the fixed-length(\verb|*lenp|) data.

Return the start address and setback \verb|*lenp| for the number of bytes read.



\textbf{\$Pop}$(*, pureptr des, stduint len)$



Pop enough bytes into the memory slice \verb|(des,len)| .



\textbf{\$Popx}$(*, stduint pos, pureptr des, stduint len)$



Pop enough bytes into the memory slice \verb|(des,len)| ,

since the position.



